%-------------------------------------------
% Himanshu Rabha - VLSI Resume
%-------------------------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\input{glyphtounicode}

\pdfgentounicode=1

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------------------------
% Custom Commands
%-------------------------------------------

\newcommand{\resumeItem}[1]{
\item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{\large #1} & \textbf{\small #2} \\
\textit{\small #3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
\small #1 & \textbf{\small #2}\\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%------------------------------------------------
% HEADER
%------------------------------------------------

\begin{center}

{\Huge \textbf{Himanshu Rabha}}

\vspace{3pt}

Assam, India

\vspace{3pt}

\small
\faPhone\ +91-7002528476
\quad
\faEnvelope\ himangshurabha10@gmail.com
\quad
\faLinkedin\ \href{https://linkedin.com/in/himanshurabha}{LinkedIn} \quad
\quad
\faGithub\ \href{https://github.com/himanshu-rabha}{GitHub}

\end{center}

\vspace{-5pt}

%------------------------------------------------
% EDUCATION
%------------------------------------------------

\section{EDUCATION}

\resumeSubHeadingListStart

\resumeSubheading
{Tezpur University}{2025 -- Present}
{M.Tech - Electronic Design and Technology}{Tezpur, Assam}

\resumeSubheading
{Central Institute of Technology Kokrajhar}{2021 -- 2025}
{B.Tech - Instrumentation Engineering}{Kokrajhar, Assam}

\resumeSubHeadingListEnd

%------------------------------------------------
% COURSEWORK
%------------------------------------------------

\section{RELEVANT COURSEWORK}

\begin{multicols}{2}
\begin{itemize}[itemsep=-2pt]

\item Physics and Technology of Semiconductor Devices
\item Advanced Semiconductor Devices
\item Advanced Logic Circuits
\item Mixed Signal Design
\item Modeling and Simulation of Digital Systems
\item Communication System Design
\item Electronic Product Design
\item Programming for Electronics Systems

\end{itemize}
\end{multicols}

\vspace{-10pt}

%------------------------------------------------
% VLSI PROJECTS
%------------------------------------------------

\section{VLSI PROJECTS}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{\underline{UART Transmitter and Receiver}} $|$ Verilog HDL, FSM Design}
{2026}

\resumeItemListStart
\resumeItem{Designed UART transmitter and receiver modules using Verilog HDL.}
\resumeItem{Implemented FSM-based communication architecture.}
\resumeItem{Developed testbench and verified functionality using simulation waveforms.}
\resumeItemListEnd

\vspace{-8pt}

\resumeProjectHeading
{\textbf{\underline{Synchronous FIFO Memory Design}} $|$ Verilog HDL}
{2026}

\resumeItemListStart
\resumeItem{Designed synchronous FIFO architecture with read/write logic.}
\resumeItem{Implemented status flag generation and buffer management.}
\resumeItem{Verified overflow and underflow conditions through simulation.}
\resumeItemListEnd

\vspace{-8pt}

\resumeProjectHeading
{\textbf{\underline{8-bit Arithmetic Logic Unit (ALU)}} $|$ RTL Design}
{2026}

\resumeItemListStart
\resumeItem{Designed arithmetic and logical operation blocks using Verilog HDL.}
\resumeItem{Implemented addition, subtraction, logical and shift operations.}
\resumeItem{Validated functionality using testbench-driven verification.}
\resumeItemListEnd

\vspace{-8pt}

\resumeProjectHeading
{\textbf{\underline{Traffic Light Controller using FSM}} $|$ Verilog HDL}
{2026}

\resumeItemListStart
\resumeItem{Designed FSM-based traffic controller with timing sequence management.}
\resumeItem{Implemented state transition logic and signal generation.}
\resumeItem{Verified behavior using simulation waveforms.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%------------------------------------------------
% ACADEMIC PROJECTS
%------------------------------------------------

\section{ACADEMIC PROJECTS}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{\underline{Solar PV Based Cooling System with MPPT Controller}} $|$ MATLAB, Simulink}
{2025}

\resumeItemListStart
\resumeItem{Designed and simulated a solar-powered cooling system using MPPT techniques.}
\resumeItem{Analyzed system efficiency under varying environmental conditions.}
\resumeItemListEnd

\vspace{-8pt}

\resumeProjectHeading
{\textbf{\underline{Speed Control of DC Motor using DC-DC Converter}} $|$ Control Systems}
{2024}

\resumeItemListStart
\resumeItem{Developed converter-based speed control system for DC motor applications.}
\resumeItem{Studied speed regulation and dynamic performance through simulation.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%------------------------------------------------
% INDUSTRIAL TRAINING
%------------------------------------------------

\section{INDUSTRIAL TRAINING}

\resumeSubHeadingListStart

\resumeSubheading
{Numaligarh Refinery Limited (NRL)}{1 Month}
{Industrial Training}{Assam}

\resumeItemListStart
\resumeItem{Observed industrial instrumentation and process control systems.}
\resumeItem{Studied sensors, transmitters, control panels and automation practices.}
\resumeItem{Gained exposure to refinery plant operations and maintenance activities.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%------------------------------------------------
% TECHNICAL SKILLS
%------------------------------------------------

\section{TECHNICAL SKILLS}

\begin{itemize}[leftmargin=0.15in,label={}]
\small{\item{

\textbf{HDLs:}
VHDL, Verilog HDL, SystemVerilog (Basic)

\\

\textbf{Digital Design:}
RTL Design, FSM Design, Combinational Logic, Sequential Logic, Timing Concepts

\\

\textbf{Semiconductor:}
Semiconductor Device Physics, CMOS Fundamentals, Mixed Signal Design

\\

\textbf{Tools:}
ModelSim, Xillinx ISE, Vivado (Basic), MATLAB, Simulink, LTSpice, Multisim, EasyEDA

\\

\textbf{Programming:}
C, Python

}}
\end{itemize}

\vspace{-10pt}

%------------------------------------------------
% INTERESTS
%------------------------------------------------

\section{AREAS OF INTEREST}

VLSI Design \quad • \quad RTL Design \quad • \quad Design Verification \quad • \quad ASIC Design Flow

FPGA Design \quad • \quad Semiconductor Devices \quad • \quad Digital System Design

\end{document}